% https://www.monash.edu/graduate-research/examination/publication
% https://www.monash.edu/rlo/graduate-research-writing/write-the-thesis
% https://www.monash.edu/rlo/graduate-research-writing/write-the-thesis/writing-the-thesis-chapters/structuring-a-long-text
\Declarationpublication{
\addtocontents{toc}{}  % Add a gap in the Contents, for aesthetics

I, Tanner Wilson, hereby declare that this thesis contains no material which has been accepted for the award of any other degree or diploma at any university or equivalent institution and that, to the best of my knowledge and belief, this thesis contains no material previously published or written by another person, except where due reference is made in the text of the thesis. 
This thesis includes two original papers published in peer-reviewed journals.
These papers are provided in Chapters~\ref{chap:subgiant_ast} and \ref{chap:stellar_spots}.
The ideas, development and writing up of all the papers in the thesis were the principal responsibility of myself, the student, working under the supervision of Associate Professor Andrew R. Casey and Professor Ilya Mandel. 
I, the student, working within the School of Physics and Astronomy under the supervision of Associate Professor Andrew R. Casey and Professor Ilya Mandel, played a majority role in contributing to the papers constituting Chapters~\ref{chap:subgiant_ast}-\ref{chap:stellar_spots}
My contributions to the papers presented in Chapters \ref{chap:subgiant_ast}-\ref{chap:stellar_spots} constitute the majority of the work required for these projects to be published.

%\input{papers/paper_table.tex}
The inclusion of co-authors reflects the fact that the work came from active collaboration between researchers and acknowledges input into team-based research.
Finally, I have not renumbered sections or page numbers of submitted and published papers in order to generate a consistent presentation within the thesis.


\textbf{Name:} Tanner Wilsoni\hspace{5.6em} \textbf{Date:} \today

\textbf{Signature:}\\
\rule[1em]{25em}{0.5pt} 


I, Andrew Casey, hereby certify that the above declaration correctly reflects the nature and extent of the student's and co-authors' contributions to this work. In instances where I am not the responsible author, I have consulted with the responsible author to agree on the respective contributions of the authors.

\textbf{Name:} Andrew Casey\hspace{5.6em} \textbf{Date:} \today

\textbf{Signature:}\\
\rule[1em]{25em}{0.5pt} 



}
